---
title: 'Do Homebuyers Care About Good Grades?: Evaluating the Effect of NYC School
Accountability Program on Housing Values'
author: "John Ihor Campagna"
date: "December 3, 2017"
output:
slidy_presentation: default
ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(ggplot2)
```

## I. Introduction/Motivation


-2006-2007 First year of New York City Progress Reports under Bloomberg

-Followed No Child Left Behind(NCLB) in 2001 under President Bush and State level in Florida and Texas in 90s

-Broadly intial Goals were to pressure schools to reform and improve student outcomes

-The nature of how the grades were implemented provided a unique discontinuity that had many applications

-The housing market is one application seeing how parents respond to an imperfect measure of school quality and what broader consequneces could be.

-NYC accountabilty program provides a large urban, and multiple ethnic context to explore the consequences

----

## I Background: School Accountability Literature

1. School Accountability Literature

Student Outcomes

-Rockoff(2010) 

-Cowen and Winters(2011)

-Elena Rouse et al(2013) 


Labor Market
-Dizon-Ross (2017)

Demographic
-Hart and Figlio (2015) 

Long Term
-Deming et al. (2016)


----

## I. Background: School Quality Literature

2.school Quality Literature

-Black(1999)

Sorting/Demographic

-Bayer et al(2007) 

-Clapp(2008)

Value Added

-Brassington and Haurin(2006) 

-Chiodo et al (2010) 

-Horn(2014) NYC choice schools

----

## II Background: School Quality and Accountability

3. School Quality and Accountability

-Figlio and Lucas(2004) 

-Ideal to get starting effects of accountability as effect appears to decrease over time

-Kane et al (2002) no effect NC, race matters black scores not as important

-Martinez (2010) effect NC



----

## III. Data

Drawn from Multiple Sources

1. NYC DOE 

- Accountability Scores

- Test Score Data

- School Demographic 

- School Zones

2. Property Data

-Property Transactions

-Property Location data

3. Cenus Data

-Likely need for neighborhood controls


----

## III. Summary Stats
```{r, echo=FALSE,warning=FALSE,fig.width=6,fig.height=4}
setwd("C:/Users/Sarah Blair/Documents/R/Schools2/rdata")
ac <- readRDS("full2.rds")

ac_11 <- filter(ac, Year == "2011", Category == "All Students", Grade == "All Grades", Grade_11 != "NA")
ac_11$Score_11 <-  as.numeric(ac_11$Score_11)

ggplot(ac_11, aes(x=Score_11, y=eng_sco))  + geom_point(aes(color = Grade_11))+  labs(title ="2011 English Scores", x = "Overall Score", y="English score") + theme(legend.position = "bottom")+ scale_colour_discrete(name  ="Accountability Grade")    
ggplot(ac_11, aes(x=Score_11, y=eng_sco))  + geom_point(aes(color = Grade_11))+  labs(title ="2011 Math Scores", x = "Overall Score", y="Math score") + theme(legend.position = "bottom")+ scale_colour_discrete(name  ="Accountability Grade")    
```

Plot of Property Values by raw school scores not grades

Same for Property Values in the school zones

Table of Property Types in neighborhood

Pretty maps of property and schools in zones etc


----

## IV. Model: Hedonic
1. Classic Hedonic
-Rosen(1974)
-Revealed preference model of estimation

$$\ ln(P_{i,z,n}) = \alpha+X_{i,n}+Z_{n}+\Gamma_{z}+e_{i,z,t} $$

-$X_{i,z}$ is a vector of Housing characteristics
-$Z_{z,n}$ is school zone characteristics
-$\gamma$ is the school quality measure 
-$\e_{i,z,t}$ error term


----

# IV. Model: BDD

2. BDD

-Black(1999)

-$Z_{z,n}$ from the hedonic model may not account for everything

-Assumes properties that are arbitrarily close to a school zone boundary have the same characristics

$$(2) \ ln(P_{i,z,b}) = \alpha+X_{i,z,b}+K_{b}+\Gamma_{z}+e_{i,z,t} $$ 
-$Z_{z,n}$ goes away replaced by $K_{b}$ which is a vector of boundary dummies
-Still may be issue as Bayer(2007) show so may still need neighborhood controls



----

# IV. Model: Fixed Effects
3. Fixed Effects

-All Accountability School Quality Papers have employed this strategey 
-Figlio(2002)...does this need to control for schools? Because of fixed effects neighborhood and invidiual prop characteristics don't need to be controlled? Add test scores as well? Only Compare A/B, B/C, C/D, D/F 




$$(3) \ ln(P_{i,n,z,m,y}) = \alpha_{i} +X_{i,z,y}+Z_{i,y}+\beta_{m} +\Gamma_{i,z,t}+e_{i,n,z,m,y} $$

-$\ln(P_{i,n,z,m,y})$ is the price for for property i, in school zone z, month m, year y

-$\alpha_{i}$ captures fixed property effects that don't change over time

-$\beta_m{m}$ are monthly dummies


Other Models
-Look at same schools where the grade has changed in a year
-Bandwiths in regards to RDD could also be used. EG really look at schools that were arbitarily close that could have recieved either A/B so compare 88-92. Can treat like regular RDD

----

## V. Problems/To Do


Problems

-Missing Earlier Data

-Problem of grade churning and changing over time

-Middle Schools

-Census Tract Data

-Distance
-Perpahs can just capture schools that are arbitrarily close to a school assuming that they are in the same school zone and at least look at what the effect year on year is e.g. What happened for schools assigned an F v those assigned a D
-Boundaries that are not natural or random i.e. a highway or river dividing a school zone